# Development + Motion with Power Dataset

## Setup

```{r setup-libraries, messages='hide', results='hide'}
library(jpeg)
source("40_montage_functions.R")
```

```{r setup-paths}
basedir <- "/home2/data/Projects/CWAS"
vizdir <- file.path(basedir, "development+motion/viz")
setwd(vizdir)
```

## Surface Maps

Below are the inflated surface maps for different development and motion CWAS. Here we used 3200 parcellations and for each parcellation, we examined how its voxelwise connectivity with the rest of the brain varied between subjects for age and if included mean FD.

There were two kinds of CWAS. In the 'standard' approach, we had two types of models that either included or did not include mean FD as a regressor. Both models had age and included the following covariates: sex and TR. We were looking to examine the effects of including motion in the model, in particular on age effects. In the 'alternative' approach, we were also looking at the effects of motion on our effects but we regressed out mean FD prior to calculating CWAS with a standard GLM. That is, at every connection the effect of motion (mean FD) was removed using GLM.

### Standard CWAS

In the 'standard' approach, we had two types of models that either included or did not include mean FD as a regressor. Both models had age and included the following covariates: sex and TR. We were looking to examine the effects of including motion in the model, in particular on age effects.

#### Only Age

```{r cwas-only-age-setup}
# Load the images
filenames.lh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_only_age_lh_(med|lat)")
filenames.rh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_only_age_rh_(med|lat)")
filenames <- c(filenames.lh, rev(filenames.rh))
images <- lapply(filenames, readJPEG)

# Coordinates
coords <- surfer_montage_coords(images, 1, 4)

# Dimensions
dims <- surfer_montage_dims(coords)
```

```{r cwas-only-age-surface, fig.width=dims$width, fig.height=dims$height}
# Visualize
invisible(surfer_montage_viz(images, coords))
```


#### Age with motion

Including motion as a covariate, reduces the extent of significant associations.

```{r cwas-age-with-motion-setup}
# Load the images
filenames.lh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_age_with_motion_lh_(med|lat)")
filenames.rh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_age_with_motion_rh_(med|lat)")
filenames <- c(filenames.lh, rev(filenames.rh))
images <- lapply(filenames, readJPEG)

# Coordinates
coords <- surfer_montage_coords(images, 1, 4)

# Dimensions
dims <- surfer_montage_dims(coords)
```

```{r cwas-age-with-motion-surface, fig.width=dims$width, fig.height=dims$height}
# Visualize
invisible(surfer_montage_viz(images, coords))
```


#### Motion with age

Many significant age associations appear overlap with associations related to motion.

```{r cwas-motion-with-age-setup}
# Load the images
filenames.lh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_motion_with_age_lh_(med|lat)")
filenames.rh <- list.files(path=vizdir, full.names=T, 
                        pattern="zpics_surface_motion_with_age_rh_(med|lat)")
filenames <- c(filenames.lh, rev(filenames.rh))
images <- lapply(filenames, readJPEG)

# Coordinates
coords <- surfer_montage_coords(images, 1, 4)

# Dimensions
dims <- surfer_montage_dims(coords)
```

```{r cwas-motion-with-age-surface, fig.width=dims$width, fig.height=dims$height}
# Visualize
invisible(surfer_montage_viz(images, coords))
```
