# Overview

This script will visualize the demographics of the discovery and replication samples.

## Setup

The base theme here builds on the `theme_tufte` in the `ggthemes` package.

```{r, messages='hide', resuls='hide'}
library(ggplot2)
library(plyr)

basedir <- "/home/data/Projects/CWAS"
sdir <- file.path(basedir, "share/age+gender/subinfo")

new_df <- read.csv(file.path(sdir, "04_all_df.csv"))

mytheme <- theme_bw() + theme(
    legend.background = element_blank(),
    legend.key        = element_blank(),
    panel.background  = element_blank(),
    panel.border      = element_blank(),
    strip.background  = element_blank(),
    plot.background   = element_blank(),
    axis.line         = element_blank(),
    panel.grid.minor  = element_blank()
)
```

## Site Summary

Here is the breakdown of the N for each site.

```{r, fig.width=15, fig.height=5}
p <- ggplot(new_df, aes(x=site, y=..count..)) + 
        geom_bar() + 
        xlab("") + 
        ylim(0,200) + ylab("Number of Participants") + 
        mytheme
p + theme(
    axis.text.x         = element_text(angle=90, vjust=0.5, hjust=1), 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

```{r}
ddply(new_df, .(site), function(x) {
    dn <- sum(x$sample=="Discovery Sample")
    rn <- sum(x$sample=="Replication Sample")
    c(
        Discovery.N = dn, 
        Replication.N = rn, 
        Difference.N = dn-rn
    )
})
```

## Sex

**Across all sites.**

```{r}
p <- ggplot(new_df, aes(sex, fill=sex)) + 
        geom_bar() + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.position     = "none", 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

**By Site.**

```{r, fig.width=15, fig.height=5}
p <- ggplot(new_df, aes(site, fill=sex)) + 
        geom_bar(position="dodge") + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.title        = element_blank(), 
    axis.text.x         = element_text(angle=90, vjust=0.5, hjust=1), 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

## Age

**Across all sites.**

```{r, fig.width=15, fig.height=5}
new_df$agegroup <- cut(new_df$age, breaks=c(18, seq(20, 80, by=10), 85), include.lowest=TRUE)
table(new_df$agegroup)

p <- ggplot(new_df, aes(age, fill=..count..)) + 
        geom_histogram(binwidth=2) + 
        xlab("Age") + 
        ylab("Number of Participants") + 
        scale_y_continuous(limits=c(0,250), expand=c(0,0)) + 
        scale_x_continuous(breaks=seq(20,80,by=20), expand=c(0,0)) + 
        mytheme
p + theme(
    legend.position     = "none", 
    panel.grid.minor.y  = element_line(colour = "grey98", size = 0.5), 
    panel.grid.major.x  = element_blank()
)
```

**By Site.**
ddply(new_df, .(site), function(x) c(table(x$agegroup)))

```{r, fig.width=16, fig.height=5}
ddply(h_new_df, .(site), function(x) table(x$handedness))

p <- ggplot(new_df, aes(site, age)) + 
        geom_violin(aes(fill=site)) + 
        xlab("") + 
        ylab("Age") + 
        scale_y_continuous(breaks=seq(20,80,by=10)) + 
        mytheme
p + theme(
    axis.text.x         = element_text(angle=90, vjust=0.5, hjust=1), 
    axis.ticks.x        = element_blank(), 
    legend.position     = "none", 
    panel.grid.minor.y  = element_line(colour = "grey98", size = 0.5), 
    panel.grid.major.x  = element_blank()
)
```

## Handedness

Note the samples (discovery vs replication) are not necessarily split evenly based on handedness. Also this dimension isn't present in all sites.

**Across all sites.**

```{r, fig.width=8, fig.height=4}
h_new_df <- subset(new_df, !is.na(handedness))

table(h_new_df$handedness)

p <- ggplot(h_new_df, aes(handedness, fill=handedness)) + 
        geom_bar() + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.position     = "none", 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

**By Site.**

```{r, fig.width=8, fig.height=4}
ddply(h_new_df, .(site), function(x) table(x$handedness))

p <- ggplot(h_new_df, aes(site, fill=handedness)) + 
        geom_bar(position="dodge") + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.title        = element_blank(), 
    axis.text.x         = element_text(angle=90, vjust=0.5, hjust=1), 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

## Eyes (Open or Closed)

Note the samples (discovery vs replication) are not necessarily split evenly based on eye status. Also this dimension isn't present in all sites.

**Across all sites.**

```{r, fig.width=8, fig.height=4}
e_new_df <- subset(new_df, !is.na(eyes))

table(e_new_df$eyes)

p <- ggplot(e_new_df, aes(eyes, fill=eyes)) + 
        geom_bar() + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.position     = "none", 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```

**By Site.**

```{r, fig.width=8, fig.height=4}
ddply(e_new_df, .(site), function(x) table(x$eyes))

p <- ggplot(e_new_df, aes(site, fill=eyes)) + 
        geom_bar(position="dodge") + 
        xlab("") + 
        ylab("Number of Participants") + 
        mytheme
p + theme(
    legend.title        = element_blank(), 
    axis.text.x         = element_text(angle=90, vjust=0.5, hjust=1), 
    panel.grid.major.y  = element_line(color="grey90", linetype="dashed"), 
    panel.grid.major.x  = element_blank(), 
    axis.ticks.x        = element_blank()
)
```
